Family Fortunes: A Quantitative Analysis of the Early Iron Age Cemeteries at Knossos, Crete

### 2019-03-29 analysis/paper/paper.Rmd
image edits

aorist_all_tombs <- colSums(main_tombs[157:206])
aorist_all_tombs<-data.frame(aorist_all_tombs)

@@

```{r aorist_uncertainty}

@@

ggplot(main_tombs,aes(total_finds))+geom_histogram()+xlim(0,200)

@@

tombs_gini<-matrix(0, ncol = 0, nrow = 1)
tombs_gini<-data.frame(tombs_gini)
for(i in colnames(aorist_tomb_values[2:51])) {
  tombs_gini[[paste0(i)]] <- ineq(aorist_tomb_vals_only[[i]],type="Gini")
}

@@

ggplot() + 
  geom_rect(data = rects, aes(xmin = xstart, xmax = xend, ymin = -Inf, ymax = Inf, fill = col), alpha = 0.4) +
     geom_line(data = tombs_gini, aes(decade,gini_coefficient))+xlim(1100,600)+ylim(0.5,0.8)+
      theme_bw()+theme(legend.title=element_blank(),
          text=element_text(family="Garamond", size=12))+
              labs(x="Date (Years BC)", y="Gini Coefficient")+
                 scale_fill_brewer(palette = "Set3")+ scale_x_reverse(expand = c(0, 0),limits=c(1100,600))+
                    scale_y_continuous(expand = c(0, 0),limits=c(0.5,0.8))

@@

no_tombs<-colSums(main_tombs[157:206]!=0)
no_tombs<-data.frame(no_tombs)
colnames(no_tombs)<-c("no_tombs")
row.names(no_tombs)<-dates
no_tombs<-data.frame(no_tombs)
setDT(no_tombs, keep.rownames = "decade")
no_tombs$decade<-as.numeric(no_tombs$decade)

@@

names(main_tombs)
tombs_in_use<-colSums(main_tombs[5:14]!="")
tombs_in_use<-data.frame(tombs_in_use)
colnames(tombs_in_use)<-c("no_tombs")
tombs_in_use<-data.frame(tombs_in_use)
setDT(tombs_in_use, keep.rownames = "period")
tombs_in_use$period<-factor(tombs_in_use$period,levels=c("SM", "EPG", "MPG", "LPG", "PGB", "EG", "MG", "LG", "EO", "LO"))

@@

tombs_ranked<-main_tombs[with(main_tombs, order(-main_tombs$total_pottery)), ]
tombs_top_12<-head(tombs_ranked,12)

>>>>

aorist_all_tombs <- colSums(tombs[157:206])
aorist_all_tombs<-data.frame(aorist_all_tombs)

@@

```{r aorist_uncertainty, fig.dim = c(7, 4)}

@@

ggplot(tombs,aes(total_finds))+geom_histogram()+xlim(0,200)

@@

tombs_gini<-matrix(0, ncol = 0, nrow = 1)
tombs_gini<-data.frame(tombs_gini)
for(i in colnames(aorist_tomb_values[2:51])) {
  tombs_gini[[paste0(i)]] <- ineq(aorist_tomb_values[[i]],type="Gini")
}

@@

ggplot() + 
  geom_rect(data = rects, aes(xmin = xstart, xmax = xend, ymin = -Inf, ymax = Inf, fill = col), alpha = 0.4) +
     geom_line(data = tombs_gini, aes(decade,gini_coefficient))+
      theme_bw()+theme(legend.title=element_blank(),
          text=element_text(family="Garamond", size=12))+
              labs(x="Date (Years BC)", y="Gini Coefficient")+
                 scale_fill_brewer(palette = "Set3")+ coord_cartesian(
                    xlim = c(1100, 600), ylim = c(0.4,0.8))+ scale_x_reverse(expand = c(0, 0),limits=c(1100,600))

@@

no_tombs<-colSums(tombs[157:206]!=0)
no_tombs<-data.frame(no_tombs)
colnames(no_tombs)<-c("no_tombs")
row.names(no_tombs)<-dates
no_tombs<-data.frame(no_tombs)
setDT(no_tombs, keep.rownames = "decade")
no_tombs$decade<-as.numeric(no_tombs$decade)

@@

names(tombs)
tombs_in_use<-colSums(tombs[5:14]!="")
tombs_in_use<-data.frame(tombs_in_use)
colnames(tombs_in_use)<-c("no_tombs")
tombs_in_use<-data.frame(tombs_in_use)
setDT(tombs_in_use, keep.rownames = "period")
tombs_in_use$period<-factor(tombs_in_use$period,levels=c("SM", "EPG", "MPG", "LPG", "PGB", "EG", "MG", "LG", "EO", "LO"))

@@

tombs_ranked<-tombs[with(tombs, order(-tombs$total_pottery)), ]
tombs_top_12<-head(tombs_ranked,12)
